### 2022-09-07 tex/Benchmark/stokes.tex
stokes

\begin{figure}
\includegraphics[width=\linewidth]{./Figures/MUMPS.pdf}
\caption{Panel a) Analysis, factorisation, solution and total solve times (panel a) and factorisation memory usage (panel b) as a function of the total number
of degrees of freedom for the Stokes flow experiment.}
\label{fig:MUMPS}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{./Figures/MUMPS.pdf}
\caption{Analysis, factorisation, solution and total solve times (panel a) and factorisation memory usage (panel b) as a function of the total number
of degrees of freedom for the Stokes flow experiment.}
\label{fig:MUMPS}
\end{figure}
